Predicting Tags for StackOverflow Posts

### 2013-06-27 stackExchange/writeups/iccm-2013/writeup.tex
Updated table data
Former-commit-id: 2a71fa469b0776f5058a458baef1052cdc7a6b03 [formerly 6acf0019a9d8e795d2b7c774a4ff1388199ed9ae]
Former-commit-id: 79116cc0f3308822344390d583498f21fa033413

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{1mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Best-fit coefficient estimates from logistic regression}
    \label{tab:coeffs}
    \vskip 0.12in
    \begin{tabular}{lllll}
      \hline
      Coefficient & 	Estimate &	Std. Err. &	z value &	$Pr(>|z|)$  \\
      \hline
      (Intercept) &	-3.00 &		0.12 &		-25.97 &	\textless2e-16 *** \\
      prior &		0.62 & 		0.01 &		66.94 & 	\textless2e-16 *** \\
      Wtitle &		0.92 &		0.02 &		39.90 &		\textless2e-16 *** \\
      Wbody &		1.76 &		0.04 &		43.21 &		\textless2e-16 *** \\
      offset &		0.78 &		0.02 &		33.25 &		\textless2e-16 *** \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{3mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Model fit metrics}
    \label{tab:fits}
    \vskip 0.12in
    \begin{tabular}{ll}
      \hline
      Common Name &  Value	\\
      \hline
      McFadden's Pseudo $R_{}^{2}$ &	.52 \\
      True Positives &			507 \\
      False Positives &			215 \\
      True Negatives &			\num{417409} \\
      False Negatives &			\num{2375} \\
      Positive Predictive Value &	0.70 \\
      Negative Predictive Value &	0.994 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

>>>>

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{1mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Best-fit coefficient estimates from logistic regression}
    \label{tab:coeffs}
    \vskip 0.12in
    \begin{tabular}{lllll}
      \hline
      Coefficient & 	Estimate &	Std. Err. &	z value &	$Pr(>|z|)$  \\
      \hline
      (Intercept) &	-2.22 &		0.10 &		-22.95 &	\textless2e-16 *** \\
      prior &		0.62 & 		0.01 &		66.94 & 	\textless2e-16 *** \\
      Wtitle &		0.93 &		0.02 &		40.00 &		\textless2e-16 *** \\
      Wbody &		1.75 &		0.04 &		43.16 &		\textless2e-16 *** \\
      offset &		0.78 &		0.02 &		33.25 &		\textless2e-16 *** \\
      \hline
    \end{tabular}
  \end{center}
\end{table}

\renewcommand{\arraystretch}{1}
\renewcommand{\tabcolsep}{3mm}
\begin{table}[!ht]
  \begin{center}
    \caption{Model fit metrics}
    \label{tab:fits}
    \vskip 0.12in
    \begin{tabular}{ll}
      \hline
      Common Name &  Value	\\
      \hline
      McFadden's Pseudo $R_{}^{2}$ &	.52 \\
      True Positives &			507 \\
      False Positives &			216 \\
      True Negatives &			\num{417408} \\
      False Negatives &			\num{2375} \\
      Positive Predictive Value &	0.70 \\
      Negative Predictive Value &	0.994 \\
      \hline
    \end{tabular}
  \end{center}
\end{table}
